Imputation of Incomplete Multilevel Data with \pkg{mice}

### 2021-11-01 Multilevel Missing Data/Multilevel Missing Data.Rmd
Add impact data

```{r, setup, include=FALSE}
options(prompt = 'R> ', continue = '+ ')
library(tidyverse)

```

@@

>>>>

```{r, setup, include=FALSE}
options(prompt = 'R> ', continue = '+ ')
library(tidyverse)
library(mice)
library(metamisc)
```

@@

- We'll use the IMPACT data (`metamisc::impact`) and simulated MNAR data (based on `mice::popularity`).

- IMPACT: A data frame with 11022 observations on the following 11 variables:
`name` Name of the study,
`type` Type of study, RCT: randomized controlled trial,OBS: observational cohort,
`age` Age of the patient,
`motor_score` Glasgow Coma Scale motor score,
`pupil` Pupillary reactivity,
`ct` Marshall Computerized Tomography classification,
`hypox` Hypoxia (0=no, 1=yes),
`hypots` Hypotension (0=no, 1=yes),
`tsah` Traumatic subarachnoid hemorrhage (0=no, 1=yes),
`edh` Epidural hematoma (0=no, 1=yes),
`mort` 6-month mortality (0=alive, 1=dead).

```{r impact}
# load data
data("impact")
# descriptive statistics
psych::describe(impact)[,c(2:5,8:9)]
```

### 2021-11-01 Multilevel Missing Data/Multilevel-Missing-Data.tex
Add impact data

\begin{itemize}
\item
  Provide practical guidelines with code snippets for imputation of
  incomplete multilevel data.
\item
  We focus on the workflow for conditional modeling (not JOMO) in
  \texttt{mice}. Refer to other packages: \texttt{mitml}.
\item
  Case study options: \texttt{metamisc::impact} (real data on traumatic
  brain injuries, IPD), \texttt{mice::popularity} (simulated data with
  MNAR/MAR mixture, schools). -\textgreater{} Check Gelman's data/NSRI
  data.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  Introduce case study and set scope of this tutorial: We're providing
  an overview of implementations. It's up-to the reader to decide which
  strategy suits their data. So we won't go into detail for the
  different methods (and equations). This paper is just a software
  tutorial. We'll keep it practical. -\textgreater{} ADD: some kind of
  help function that suggests a suitable pred matrix to the user, given
  a certain analysis model.
\end{itemize}

@@

\begin{itemize}
\item
  JOMO in mice --\textgreater{} on the side for now
\item
  Additional levels of clustering
\item
  Timeseries: and polynomial relationship in the clustering.
\end{itemize}

>>>>

\begin{itemize}
\item
  Provide practical guidelines with code snippets for imputation of
  incomplete multilevel data.
\item
  We focus on the workflow for conditional modeling (not JOMO) in
  \texttt{mice}. Refer to other packages: \texttt{mitml},
  \texttt{miceadds}.
\item
  Case study options: \texttt{metamisc::impact} (real data on traumatic
  brain injuries, IPD), \texttt{mice::popularity} (simulated data with
  MNAR/MAR mixture, schools). -\textgreater{} Check Gelman's data/NSRI
  data.
\item
  Introduce case study and set scope of this tutorial: We're providing
  an overview of implementations. It's up-to the reader to decide which
  strategy suits their data. So we won't go into detail for the
  different methods (and equations). This paper is just a software
  tutorial. We'll keep it practical. -\textgreater{} ADD: some kind of
  help function that suggests a suitable pred matrix to the user, given
  a certain analysis model.
\end{itemize}

@@

\begin{itemize}
\item
  We'll use the IMPACT data (\texttt{metamisc::impact}) and simulated
  MNAR data (based on \texttt{mice::popularity}).
\item
  IMPACT: A data frame with 11022 observations on the following 11
  variables: \texttt{name} Name of the study, \texttt{type} Type of
  study, RCT: randomized controlled trial,OBS: observational cohort,
  \texttt{age} Age of the patient, \texttt{motor\_score} Glasgow Coma
  Scale motor score, \texttt{pupil} Pupillary reactivity, \texttt{ct}
  Marshall Computerized Tomography classification, \texttt{hypox}
  Hypoxia (0=no, 1=yes), \texttt{hypots} Hypotension (0=no, 1=yes),
  \texttt{tsah} Traumatic subarachnoid hemorrhage (0=no, 1=yes),
  \texttt{edh} Epidural hematoma (0=no, 1=yes), \texttt{mort} 6-month
  mortality (0=alive, 1=dead).
\end{itemize}

\begin{CodeChunk}
\begin{CodeInput}
R> # load data
R> data("impact")
R> # descriptive statistics
R> psych::describe(impact)[,c(2:5,8:9)]
\end{CodeInput}
\begin{CodeOutput}
                 n  mean    sd median min max
name*        11022  8.32  4.37      8   1  15
type*        11022  1.73  0.44      2   1   2
age          11022 34.93 15.89     31  14  93
motor_score* 11022  2.59  1.18      3   1   4
pupil*       11022  1.46  0.71      1   1   3
ct*          11022  1.98  0.89      2   1   3
hypox        11022  0.22  0.41      0   0   1
hypots       11022  0.17  0.38      0   0   1
tsah         11022  0.45  0.50      0   0   1
edh          11022  0.13  0.34      0   0   1
mort         11022  0.26  0.44      0   0   1
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{itemize}
\item
  JOMO in \texttt{mice} --\textgreater{} on the side for now
\item
  Additional levels of clustering
\item
  Timeseries: and polynomial relationship in the clustering.
\end{itemize}
